\documentclass[final,a4paper,oneside,12pt]{article}
\setlength{\parindent}{0in}
 \usepackage{verbatim}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\begin{comment}
\usepackage[OT2,T1]{fontenc}
\DeclareSymbolFont{cyrletters}{OT2}{wncyr}{m}{n}
\DeclareMathSymbol{\Sha}{\mathalpha}{cyrletters}{"58}
\end{comment}
\usepackage{geometry}
%% Alex's thing
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\linespread{1}

\geometry{
  body={7in, 10in},
  left=0.6in,
  top=0.5in
}

\setlength\parindent{0em}

\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{*1}{*1}
\titlespacing{\subsection}{1pt}{*0.8}{*0.8}
\titlespacing{\subsubsection}{0pt}{*0}{*0}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[pdftex]{graphicx}
\usepackage{fullpage}
%%%
\begin{document}

\centerline{\Large \bf{Rise 2011 Report}}
\bigskip
\centerline{James McMurray}
\bigskip


\emph{I agree that my report and accompanying pictures may be used by the DAAD in printed materials, presentations, and on websites in order to inform funding organisations, sponsors, and students about the RISE programs (RISE, RISE pro and RISE worldwide).}\\

When I was first accepted on to the RISE programme, I was worried that the language barrier would be a great problem, and that I would struggle to find accommodation in time, fortunately neither of these worries proved true, mostly due to the great hospitality shown by those I met. \\

Prior to leaving England, I emailed my PhD student supervisor and we discussed accommodation, eventually he found one of his friends who had needed someone to sublet with him as his flatmate was working abroad. However, because the other flatmate didn't leave until July, my PhD supervisor let me stay in his apartment for the last week of June when I first arrived in Konstanz.\\

Before starting my internship, the DAAD provided a 2-week language course in Munich which I was able to attend. This was fortunate, since my twin brother was also on the RISE programme (although working far away in Berlin), and so it meant I didn't have to leave England alone. The language course was one of the best parts of my time in Germany, I made good friends with someone on the language course who worked in Munich and we would later visit Ulm and Basel together. Coincidentally, one of the students who was also working near Konstanz happened to be working in Munich for the start of her internship, and so it also gave me a great opportunity to meet someone who I was able to see regularly when working in Konstanz.\\

The language course was excellent, the teachers were friendly and I learnt a good amount of German given it was the first time I'd studied it. The language school also provided a trip to Dachau and the Augustiner Brewery which were both interesting. I also took the opportunity to visit Salzberg and Herrenchiemsee with the other language school students, and the various attractions in Munich such as the Nymphenburger Palace, Hofbrauhaus, Englischer Garten and the art museums. My host family were also very welcoming and were helpful in recommending places to visit in Munich and around Konstanz too.\\

%After arriving in Konstanz, I opened a bank account with Deutsche Bank. Fortunately this was very simple and took only about an hour. 

When I first started my internship, my PhD student supervisor explained the basics of the project the research group had been working on and gave me some papers to read to understand the basics. For the first week, I read these papers and watched the other workers going through the standard processes in the small laboratory and clean room.

\end{document}